Initial spatial conditions in simulation models: the missing leg of sensitivity analyses?

### 2017-11-02 paper.tex
Update on Overleaf.

%%%%%%%%%%%%%
\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/relativedistance_metaparams}\\
%\includegraphics[width=0.4\textwidth]{figures/alpha_beta_schemas}(Bottom) Corresponding stylised density grids\\\comment[JR]{je sais pas si c'est une bonne idee de mettre les grilles stylisees comme ca parce que ca donne une fausse idee des sorties du modele de generation}}
\caption{\textbf{Relative distances of phase diagrams by initial spatial grids described by the meta-parameters of their generator.} Relative distance as a function of meta-parameters $\alpha$ (strength of preferential attachment) and $\beta$ (strength of diffusion process).
\label{fig:sugarscape-distance-meta}
\end{figure}
%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%
\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/relativedistance_metaparams}\\
%\includegraphics[width=0.4\textwidth]{figures/alpha_beta_schemas}(Bottom) Corresponding stylised density grids\\\comment[JR]{je sais pas si c'est une bonne idee de mettre les grilles stylisees comme ca parce que ca donne une fausse idee des sorties du modele de generation}}
\caption{\textbf{Relative distances of phase diagrams by initial spatial grids described by the meta-parameters of their generator.} Relative distance as a function of meta-parameters $\alpha$ (strength of preferential attachment) and $\beta$ (strength of diffusion process).}
\label{fig:sugarscape-distance-meta}
\end{figure}
%%%%%%%%%%%%%
